PROTEST

### 2019-09-04 article/main.tex
dg calculation proof

\section*{Journal}
\begin{itemize}
    \item Environmental Modelling \& Software (suggestion Patrick)
    \item Agricultural and Forest Meteorology (Coupling transversal and longitudinal models to better predict Quercus petraea and Pinus sylvestris stand growth under climate change)
    \item Forest Ecology and Management
    \item Annals of Forest Science (Capsis: an open software framework and communityfor forest growth modelling)
    \item Journal of Environmental Management
\end{itemize}

@@

\subsection*{Landscape initialisation}
To run SIMMEM simulations, the following variables must be available for each forest plot:
\begin{itemize}
    \item site index
    \item composition
    \item species basal area
    \item species quadratic diameter
\end{itemize}

@@

\subsection*{Composition initialisation}

We assigned a composition to all forest plots over the study area following a five-step procedure:

@@

    \item We then classified all the forest plots over the study area into 3 composition types: deciduous, coniferous or deciduous-coniferous mixture. For that we used a LIDAR-derived measure: the proportion of deciduous basal area ($P_{Gd}$). Plots in which the deciduous basal area accounted for more than 75\% of the total basal area were classified as deciduous. Conversely, plots in which the deciduous basal area accounted for less than 25\% of the total basal area were classified as coniferous. The remaining plots were classified as deciduous-coniferous mixture.

@@

\subsection*{Basal area}

\noindent We relied on two LIDAR-derived measures to assign species basal area values ($G_{sp}$) to each forest stand: the stand total basal area ($G_t$) and the proportion of deciduous basal area ($P_{Gd}$). $G_{sp}$ could directly be derived from these measures for pure stands and deciduous-coniferous mixtures (i.e. beech-fir and beech-spruce stands). We developped a two-step procedure to assign $G_{sp}$ to conifer mixtures (i.e. fir - spruce mixtures):

@@

  \item We first modeled the proportion of $G_{fir}$ in the PROTEST plots, from environmental variables and LIDAR-derived measures (and modeled site index???) as follows:

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ were parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we used the $G_{fir}$ and $G_{spruce}$ obtained after the grouping of species (i.e. after having assigned the basal area of non-target species to the target species; see the \textit{composition initialisation} section).

  \item We then calculated the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model prediction a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. $G_{spruce}$ was obtained by substracting $G_{fir}$ to $G_t$.

@@

\subsection*{Quadratic diameter}

We calculated species quadratic diameter in different ways depending on the stand type:

\begin{enumerate}
    \item In the case of pure stands, the total quadratic diameter ($Dg_t$) measured by LIDAR was directly used.

    \item In the case of mixed stands, we adopted a XXX-step procedure:
    \begin{enumerate}
        \item We first modeled the link between the species quadratic diameters in each mixture as follows:

            \begin{equation}\label{}
            \frac{Dg_1}{Dg_2} = a = \alpha + \beta_1 alti + \beta_2 pH +\beta_3 rum +\beta_4 slope +\beta_5 rocheCalc+...+\varepsilon
             \end{equation}
           where $Dg_1$ and $Dg_2$ are the quadratic diameters of species 1 and 2.

           --> data: true mixtures from protest plots (i.e. Gsp1 + Gsp2 > 0.75Gt)
           --> variable selection
           --> see final models in SI

        \item We then calculated the quadratic diameter for one species from a set of two equations linking species basal area to species quadratic diameter:

        \begin{equation}\label{}
      G_i = \frac{n_i\pi D_i^2}{4}
        \end{equation}
        where $G_i$, $D_i^2$ and $n_i$ are the basal area, the quadratic diameter and the number of individuals of species $i$, respectively. $G_i$ is directly obtained from LIDAR measures.

        \begin{equation}\label{}
        D_t^2 = \frac{n_1Dg_1^2 + n_2Dg_2^2}{n_1 + n_2}
        \end{equation}
        where $D_t^2$ is the total quadratic diamater of the stand (obtained from LIDAR measures). $n_1$ and $n_2$ correspond to the number of individuals of species 1 and 2, respectively.

\noindent solution--> see proof i annexe

        \item We finally calculated the species quadratic diameter for the second species
    \end{enumerate}
\end{enumerate}

Here, we relied on a single LIDAR measure to assign species quadratic diameter values to each forest stand: the total quadratic diameter ($Dg_t$).

---> calibration
---> prédiction + random dans (var(epsi)

@@

>>>>

\section*{Journal}
\begin{itemize}
    \item Environmental Modelling \& Software (suggestion Patrick)
    \item Agricultural and Forest Meteorology (Coupling transversal and longitudinal models to better predict Quercus petraea and Pinus sylvestris stand growth under climate change)
    \item Forest Ecology and Management
    \item Annals of Forest Science (Capsis: an open software framework and communityfor forest growth modelling)
    \item Journal of Environmental Management
    \item Methods in ecology and evolution (papier sur méthode d'initialisation)
\end{itemize}

@@

\subsection*{Landscape initialisation}
To run SIMMEM simulations, the following variables must be available for each forest plot:
\begin{itemize}
    \item site index
    \item composition
    \item species basal area
    \item number of trees per species (species quadratic diameter must be calculated for that)
\end{itemize}

@@

\subsection*{Composition}

We assigned a composition to all forest plots over the study area following a four-step procedure:

@@

    \item We then classified all the forest plots over the study area into 3 composition types: deciduous, coniferous or deciduous-coniferous mixture. For that we used the proportion of deciduous basal area ($P_{Gd}$) calculated from LIDAR data. Plots in which the deciduous basal area accounted for more than 75\% of the total basal area were classified as deciduous. Conversely, plots in which the deciduous basal area accounted for less than 25\% of the total basal area were classified as coniferous. The remaining plots were classified as deciduous-coniferous mixture.

@@

\subsection*{Species basal area}

\noindent We assigned species basal area values ($G_{sp}$) to each forest stand using the stand total basal area ($G_t$) and the proportion of deciduous basal area ($P_{Gd}$) calculated from LIDAR data. $G_{sp}$ could directly be derived from these measures for pure stands and deciduous-coniferous mixtures (i.e. beech-fir and beech-spruce stands). We developed a two-step procedure to assign $G_{sp}$ to conifer mixtures (i.e. fir - spruce mixtures):

@@

  \item We first modeled the proportion of $G_{fir}$ in the PROTEST plots from environmental variables and LIDAR-derived measures (and modeled site index???) as follows:

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we used the $G_{fir}$ and $G_{spruce}$ obtained after the grouping of species (i.e. after having assigned the basal area of non-target species to the target species; see the \textit{composition initialisation} section).

  \item We then calculated the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. $G_{spruce}$ was obtained by substracting $G_{fir}$ to $G_t$.

@@

\subsection*{Species quadratic diameter}\label{Dg}

We assigned species quadratic diameter ($Dg_{sp}$) in different ways depending on the stand composition. In the case of pure stands, we directly used the total quadratic diameter ($Dg_t$) calculated from LIDAR data. We developed a three-step procedure for mixed stands:

  \item We first modeled the species quadratic diameters ratio in the PROTEST plots (separately for each mixture, i.e. beech-fir, beech-spruce and fir-spruce) from environmental variables and LIDAR-derived measures (and modeled site index???) as follows:

  \begin{equation}\label{DgModel}
    \frac{Dg_i}{Dg_j} = \alpha + \beta_1 alti + \beta_2 pH +\beta_3 rum +\beta_4 slope +\beta_5 rocheCalc+...+\varepsilon
  \end{equation}

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three final models in SI).

  \item We then calculated $r_{Dg}$, the $Dg_i / Dg_j$ ratios for all mixed stand over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals.

  \item We then calculated the species quadratic diameter using two equations linking species basal area to species quadratic diameter:

  \begin{equation}\label{}
    G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
  \end{equation}

  where $G_{sp}$, $D_{sp}$ and $n_{sp}$ are the basal area, the quadratic diameter and the number of individuals of a species, respectively; and

  \begin{equation}\label{}
    Dg_t^2 = \frac{n_iDg_i^2 + n_jDg_j^2}{n_i + n_j}
  \end{equation}

  where $Dg_t$ is the total quadratic diamater of a stand; $Dg_i$ and $Dg_j$, the quadratic diameters of species $i$ and $j$; and $n_i$ and $n_j$, the number of individuals of species $i$ and $j$. $Dg_i$ could therefore be expressed as:

  \begin{equation}\label{}
    Dg_i = Dg_t\sqrt{\frac{G_i + r_{Dg}^2G_j}{G_i + G_j}}
  \end{equation}

  where $G_i$ and $G_j$ are the species basal area (see proof in SI). We finally calculated $Dg_j$ as follows:

  \begin{equation}\label{}
    Dg_j = \frac{Dg_i}{a}
  \end{equation}

--> on s'est assuré que les a et b soient dans un interval de valeur défini

\subsection*{Number of trees per species}

@@

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{SUPPORTING INFORMATION}

\clearpage

\noindent Proof: calculating species quadratic diameters from a set of three equations

\noindent The three starting equations are as follows

\begin{equation}\label{one}\tag{1}
  \bullet G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
\end{equation}

\noindent where $G_{sp}$, $D_{sp}$ and $n_{sp}$ are the basal area, the quadratic diameter and the number of individuals of a species, respectively.

\begin{equation}\label{}\tag{2}
  \bullet Dg_t^2 = \frac{n_iDg_i^2 + n_jDg_j^2}{n_i + n_j}
\end{equation}

\noindent where $Dg_t$ is the total quadratic diamater of a stand; $Dg_i$ and $Dg_j$, the quadratic diameters of species $i$ and $j$; and $n_i$ and $n_j$, the number of individuals of species $i$ and $j$.

\begin{equation}\label{three}\tag{3}
  \bullet \frac{Dg_i}{Dg_j} = r_{Dg}
\end{equation}

\noindent where $r_{Dg}$ is calculated by adding to the models predictions (described at eqn \ref{DgModel}) a random number (see the \textit{Species quadratic diameter} section).

\hfill

\noindent Using equation \ref{one}, $Dg_t^2$ can be expressed as:

\begin{equation*}\label{}
  Dg_t^2 = \frac{\frac{4}{\pi}G_i + \frac{4}{\pi}G_j}{\frac{4G_i}{\pi Dg_i^2} + \frac{4G_j}{\pi Dg_j^2}}
\end{equation*}

\begin{equation*}\label{}
  Dg_t^2 = \frac{G_i + G_j} {\frac{G_i}{Dg_i^2} + \frac{G_j}{Dg_j^2}}
\end{equation*}

\begin{equation*}\label{}
  Dg_t^2(\frac{G_i}{Dg_i^2} + \frac{G_j}{Dg_j^2})= G_i + G_j
\end{equation*}

\begin{equation*}\label{}
  Dg_t^2(G_i + \frac{Dg_i^2}{Dg_j^2}G_j^2)= Dg_i^2(G_i + G_j)
\end{equation*}

\noindent Using equation \ref{three}, $Dg_i^2 / Dg_j^2$ can be replaced by $r_{Dg}^2$:

\begin{equation*}\label{}
  Dg_t^2(G_i + r_{Dg}^2G_j^2)= Dg_i^2(G_i + G_j)
\end{equation*}

\noindent hence:

\begin{equation*}\label{}
  Dg_i = Dg_t\sqrt{\frac{G_i + r_{Dg}^2G_j}{G_i + G_j}}
\end{equation*}
